\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{amssymb}

\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

\pagestyle{empty}

% Adjust section spacing
\titleformat{\section}{\Large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{2pt}{2pt}

% Set margins
\setlength{\tabcolsep}{0em}
\setlength{\parindent}{0em}
\setlength{\parskip}{0.5em}

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \textbf{#1} \hfill {#2} \\
    \emph{#3} \hfill {#4} \\
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}}
\renewcommand{\labelitemii}{$\circ$"}

\begin{document}

%----------HEADER-----------------
\begin{center}
    {\LARGE \textbf{Monojit Mandal}}\\
    \href{mailto:monojitmandal333@gmail.com}{monojitmandal333@gmail.com} $|$ +91-8272966790 $|$ 
    \href{https://www.linkedin.com/in/monojitmandal/}{linkedin.com/in/monojitmandal} $|$ 
    \href{https://github.com/yourgithub}{github.com/yourgithub} $|$ Kolkata, India
\end{center}

%----------SUMMARY----------------
\section*{Summary}
Data Scientist with 5+ years of experience in building data-driven solutions using machine learning, statistical and mathematical modeling, and data visualization. Proven expertise in Python, SQL, and Cloud platforms. Strong background in delivering actionable business insights and developing scalable models for production environments.

%----------SKILLS-----------------
\section*{Skills and Expertise}
\textbf{Languages:} Python, R, SQL \\
\textbf{Libraries/Frameworks:} pandas, NumPy, scikit-learn, TensorFlow, PyTorch, Polars, Matplotlib, Seaborn \\
\textbf{Tools/Platforms:} Jupyter, Git, Docker, MLflow, Airflow, Streamlit, FastAPI \\
\textbf{Databases/Cloud:} MSSQL, Oracle, BigQuery, GCP (Vertex AI)\\
\textbf{Domain/Function:} Manufacturing Analytics, Supply Chain Analytics, Reliability Modeling, Operations Research, Machine Learning, NLP

%----------EXPERIENCE-------------
\section*{Professional Experience}
\begin{itemize}
    \resumeSubheading
      {Decision Scientist, Supply Chain}{June 2024 -- Present}
      {Accenture}{Kolkata, India}
      \begin{itemize}
          \resumeItem{
            Developed an Inventory to Order matching algorithm for a Steel Manufacturer to optimize yield, 
            Inventory and Service Leve using a Multi Objective Greedy Heuristic based optimization model. 
            Considering dimension, quality and chemistry as matching criteria, model was able to pick the 
            best order for inventories leading to $\sim$2.5\% better yield and selected older materials ($\sim$7 days) 
            to older coils ($\sim$ 14 days) to reduce risk of material degradation and risk of not meeting target 
            date for orders when compared against existing manual process.
            }
          \resumeItem{
            Developed a Vendor Negotiation chatbot for big Retailers/FMCG/CPG to help automate negotiations with tail
            spend suppliers (low volume/transaction) to help automate negotiations. Agentic Architecture with LLM was used to understand priority levers in
            the negotiation process and based on set parameters it finds competitive offers for suppliers.
          }
          \resumeItem{
            Developed a POC MILP model for an energy retailer/distributor company to optimize Vessel Routing and
            Scheduling process more efficiently to reduce Fixed Cost, Port operating cost, Demurrage Cost while
            considering multiple factors like Inventory levels, Vessel utilization, port demand, berth availability etc
          }
      \end{itemize}

    \resumeSubheading
      {Data Scientist, Supply Chain}{Mar 2021 -- June 2024}
      {General Mills}{Mumbai, India}
      \begin{itemize}
          \resumeItem{
            Developed a MILP model to recommend daily optimal production plan of Snacks for a year horizon in such a
            way that total Changeover time is minimum, and inventory level is balanced (balancing stockout and overflow).
            This tool can potentially save $\sim\$$2 MM/Year for a Manufacturing Line by reducing average inventory by $\sim$25 \%
            and reducing changeover time by $\sim$15 \%
          }
          \resumeItem{
            Reduction of Manufacturing waste in Refrigerated Frozen Baked Goods product by recommending optimal
            controlling parameter ranges during the manufacturing process, leading to savings of $\sim\$$8 M/Year. Generalized
            Linear Model (Poisson’s Regression) used to establish the relationship between Reject and controlling
            parameters with R square of $\sim$50 \%.
          }
          \resumeItem{
            Developed Ramp Up Analysis tool (self-serve) to improve System Reliability of Manufacturing Systems by
            $\sim\$$1.5\% leading to potential savings of $\sim\$$ 9 MM/Year. Using the mean shift Changepoint algorithm Ramp Up
            and post Ramp Up phase were identified. A self-serve Dash App was developed to share actionable insights
            to System Engineers and root cause analysis.
          }
          \resumeItem{
            Developed Ramp Up Analysis tool (self-serve) to improve System Reliability of Manufacturing Systems by
            $\sim$1.5\% leading to potential savings of $\sim\$$ 9 MM/Year. Using the mean shift Changepoint algorithm Ramp Up
            and post Ramp Up phase were identified. A self-serve Dash App was developed to share actionable insights
            to System Engineers and root cause analysis.
          }
          \resumeItem{
            Minimizing waste of Hard Taco Shell product using CART Model resulting in potential $\sim\$$ 1 MM savings in a
            Year. Decision Tree, Random Forrest, XGBoost, Gradient Boost models are applied and compared with respect
            to R2 metric and finally Decision Tree model was selected because of explainability. With R2 value of 0.6 the
            model was able to recommend an optimal operating range of mixing and processing parameters.
          }
          \resumeItem{
            Developed a tool to minimize overuse/overpack waste and providing visibility to Operators helped to save yearly 
            $\sim\$$ 100,000 in a Manufacturing Line. MILP Optimization algorithm is used to optimize time to stop processing
            system to balance surge while completing target production on time.
          }
          \resumeItem{
            Developed an automated ML based approach to help Capacity Planners to understand whether Supply Chain
            planning (horizon 24 months) needs to be revised or not, which can lead to savings of 300 employee hours per
            month.
          }
          \resumeItem{
            Developed a Bid Variance Dashboard using Tableau to help Transportation leaders to identify root causes of
            difference in actual and bid numbers. Also, this provides a direction to the future scenario of bid considering
            extension of current bid split.
          }
      \end{itemize}
    
    \resumeSubheading
      {Analytics Consultant}{Nov 2020 -- Mar 2021}
      {EXL Analytics}{Gurugram, India}
      \begin{itemize}
          \resumeItem{
            Developed a Power BI dashboard and self-serve data model for an eyeglass retailer Company to improve
            marketing campaign of product and acquiring new customer, tracking sales, profit, margin etc. in real time
            manner.
          }
      \end{itemize}

    \resumeSubheading
      {Data Analyst Intern}{July 2019 -- Dec 2019}
      {Tata Steel}{Kalinganagar, India}
      \begin{itemize}
          \resumeItem{
            Reducing 80 to 85\% of waste in byproduct gases produced during steel making process with the help of MILP
            Optimization model. Time dependent parameters are estimated using complex ensembled based model (HP-LSTM-LSSVM).
          }
      \end{itemize}
\end{itemize}

%----------PROJECTS---------------
\section*{Acadenic Projects}
\begin{itemize}
    \resumeSubheading
      {Automotive Domain Specific Sentiment Analysis using NLP}{}
      {Python, nltk, scikit-learn}{}
      \begin{itemize}
        \resumeItem{
          Developed domain specific sentiment dictionary to improve Sentiment Analysis ML Algorithms using NLP. Used
          Amazon Automotive data to build domain specific corpus and updated sentiment scores of Sentiwordnet
          dictionary. With new domain specific corpus F1 score improved by 5-10 \%
        }
      \end{itemize}

    \resumeSubheading
      {Supply Chain Network Strategy of a Retail Company}{}
      {Python, CPLEX}{}
      \begin{itemize}
      \resumeItem{
        Designed a Supply Chain Network of a new company which wanted to launch a product in a new city. With
        survey data demand is forecasted and with all cost inputs (fixed \& variable cost in manufacturing, truck cost,
        minivan cost, holding cost) a robust optimal network is built, and strategy of replenishment is developed using
        MILP Optimization model to minimize total cost of Supply Chain.
      }
      \end{itemize}

\end{itemize}

%----------EDUCATION--------------
\section*{Education}
\begin{itemize}
  \resumeSubheading
    {M.Tech in Industrial Engineering, IIT Kharagpur}{June 2018 -- June 2020}
    {Grade: 9.76 out of 10}{Kharagpur, India}
    \begin{itemize}
      \resumeItem{
        Relevant Coursework: Statistical Decision Modeling, Operations Research, Supply Chain Management, Production Planning and Inventory Control, 
        Applied Multivariate Statistical Modelling, Stochastic Modelling
      }
    \end{itemize}
\end{itemize}
\begin{itemize}
  \resumeSubheading
    {B.Tech in Mechanical Engineering, GCETTB}{June 2014 -- June 2018}
    {Grade: 8.71 out of 10}{Berhampore, India}
\end{itemize}
\begin{itemize}
  \resumeSubheading
    {Higher Secondary in Science, BNGHS}{June 2012 -- June 2014}
    {Grade: 76.4\%}{Kolkata, India}
\end{itemize}
\begin{itemize}
  \resumeSubheading
    {Secondary, LHV}{June 2012 -- June 2014}
    {Grade: 83.4\%}{Kolkata, India}
\end{itemize}

%----------CERTIFICATIONS---------
\section*{Certifications}
\begin{itemize}
    \item Machine Learning | Stanford University
    \item Deep Learning | Deeplearning.ai
    \item Convolutional Neural Network | Deeplearning.ai
    \item Sequential Models | Deeplearning.ai
    \item Natural Language Processing with Tensorflow | Deeplearning.ai
    \item SQL for Data Science | UC Davis
    \item Introduction to Probability \& Data with R | Duke University
    \item Algorithmic Toolbox | UC San Diego
    \item Programming Foundation with Javascripts, HTML, CSS | Duke University
    \item Linear Regression Modelling with R | Duke University
    \item Java Programming | Solving Problems with Software | Duke University
    \item Inferential Statistics with R | Duke University
    \item Data Analytics Rapid Training Program | Great Learning
    \item Generative AI with Large Language Models | Deeplearning.ai 
\end{itemize}

%----------AWARDS---------------
\section*{Achievements \& Awards}
\begin{itemize}
    \item Rookie of Quarter | General Mills | 2021
    \item Value Creator | General Mills | 2021
    \item Shining Star | General Mills | 2021
    \item Analytics Champion | General Mills | 2021
    \item Runner up in Datalympics (Global level event)| General Mills | 2021
    \item Runner up in Supply Chain Analytics Hackathon | General Mills | 2022
    \item Runners Up in Innovation Challenge Competition in Supply Chain | General Mills | 2022
    \item Way of Working Award | General Mills | 2023
    \item Suply Chain Ninja Award | General Mills | 2023
    \item Above and Beyond | Accenture | 2025
\end{itemize}

\end{document}
